### 2021-03-09 research project/sections/Analysis_of_results.tex
final rp draft
rp work

The iterations needed for both methods were also measured, using the Python program
(see appendix), slightly modified to increment a variable \verb|i| and subsequently
return it, writing it in a similar manner to a \verb|.csv| file.

@@

Shown below is a graph demonstrating the correlation between the decimal places approximated
and the amount of iterations needed for this specific decimal milestone. The blue markers and
line of best-fit respresent the results received from Viète's method while the red represent those
from Madhava's method. \\

>>>>

The iterations needed for the approximation to a decimal place of both methods were also measured, using the Python program (see appendix), slightly modified to increment a variable \verb|i| and subsequently return it, writing it in a similar manner to a \verb|.csv| file.

@@

Shown below is a graph demonstrating the correlation between the decimal places approximated and the amount of iterations needed for this specific decimal milestone. The blue markers and line of best-fit represent the results received from Viète's method while the red represent those from Madhava's method.

### 2021-03-09 research project/sections/Background.tex
final rp draft
rp work

And because $\frac{\sin{\theta}}{\cos{\theta}} = \tan{\theta}$, the aforementioned expression
can be simplified to:

@@

$\frac{A_{n}}{\cos{\alpha} \cos{\frac{\alpha}{2}} \cos{\frac{\alpha}{4}} \dots}
  \to_{k \to \infty} \pi$

@@

So it can be said that $U_{n} = \sqrt{\frac{1}{2} + \frac{1}{2} U_{n - 1}}$, which leads to a fully defined expression for the value of pi, using an infinite product:

>>>>

And because $\frac{\sin{\theta}}{\cos{\theta}} = \tan{\theta}$, the expression
can be simplified to:

@@

$\frac{A_{n}}{\cos{\alpha} \cos{\frac{\alpha}{2}} \cos{\frac{\alpha}{4}} \dots}\to_{k \to \infty} \pi$

@@

$U_{n} = \sqrt{\frac{1}{2} + \frac{1}{2} U_{n - 1}}$, which leads to a fully defined expression for the value of pi, using an infinite product:

### 2021-03-09 research project/sections/Computational_approach.tex
final rp draft
rp work

\subsection{The variables}
The dependent variable of this experiment is the time taken $t$ by the program
to approximate a given number $n$ of correct decimal value of the constant $\pi$.

@@

A Python application was programmed (see appendix) in order to run the two
methods aforementioned, and manage the collection of data.

>>>>

\subsection{The variables}
The dependent variable of this experiment is the time taken $t$ by the program to approximate a given number $n$ of correct decimal values in the constant $\pi$.

@@

A Python application was programmed (see appendix) in order to run the two methods, and manage the collection of data.

### 2021-03-09 research project/sections/Conclusion.tex
final rp draft
rp work

An example of this kind of difference in computing power 
needed for different mathematical operations can be seen in the video-game \textit{Quake III Arena}, published in 1999. 
The inverse square root of a number needed to be calculated, however due to performance issues, the standard 
function could not be used. And as such, a new function for the approximation of the inverse square root of a number 
was programmed \cite{id-software_2012}, highly more efficient than the old one, which shows that a mathematical function 
implemented in computing can be more efficient than another.

>>>>

An example of this kind of difference in computing power needed for different mathematical operations can be seen in the video-game \textit{Quake III Arena}, published in 1999. The inverse square root of a number needed to be calculated, however due to performance issues, the standard function could not be used. And as such, a new function for the approximation of the inverse square root of a number was programmed \cite{id-software_2012}\cite{beyond3d_2006}, highly more efficient than the old one, which shows that a mathematical function implemented in computing can be more efficient than another.

### 2021-03-09 research project/sections/Further_research.tex
final rp draft
rp work

This paper does not discuss the many advantages of efficient code in detail, 
and a research on the speed of the mathematical functions in programming could 
be conducted. Computer program efficiency is always a pertinent topic because 
of a faster and faster world. An example of this could be the company Amazon, 
whose production speed has skyrocketed during the last decade. An increasingly 
fast demand also requires an increasingly fast computing infrastructure; to handle 
shipments, manage customers or even conduct job interviews (an experimental system that received 
major backlash in 2018). \cite{murad_2021}

>>>>

This paper does not discuss the many advantages of efficient code in detail, and a research on the speed of the mathematical functions in programming could be conducted. Computer program efficiency is always a pertinent topic because of a faster and faster world. An example of this could be the company Amazon, whose production speed has skyrocketed during the last decade. An increasingly fast demand also requires an increasingly fast and accurate computing infrastructure; to handle shipments, manage customers or even conduct job interviews (an experimental system that received major backlash in 2018). \cite{murad_2021}

### 2021-03-09 research project/sections/Introduction.tex
rp
rp work
final rp draft

This paper seeks to examine the extent at which two historical methods of
approximation of the value $\pi$, namely the approaches suggested by the aforementioned 
mathematicians Madhava and Viète, differ in terms of computational speed and 
speed, and explain these differences. This paper does not however, 
suggest a method to use for computation but rather seeks to only compare 
the speed of a geometrically derived formula and a analytically derived one.

This research could prove useful in the field of computer science, as 
there is always a demand for faster and more efficient programs in an
ever-changing society.

Furthermore, a research based on computational speed of two different 
kinds approaches to the constant $\pi$ has not been done to date.

>>>>

This paper seeks to examine the extent at which two historical methods of approximation of the value $\pi$, namely the approaches suggested by the mathematicians Madhava and Viète, differ in terms of computational speed, and explain these differences. This paper does not however, suggest a method to use for computation but rather seeks to only compare the speed of a geometrically derived formula and a analytically derived one.

This research could prove useful in the field of computer science, as there is always a demand for faster and more efficient programs in an ever-changing society. Furthermore, a research based on computational speed of two different kinds approaches to the constant $\pi$ has not been done to date.
